### 2014-12-08 Draft/introduction.tex
updated based on Dr. Xie's Comments

Application Programming Interfaces (APIs) have evolved from traditional libraries that are in the format of locally stored binary files and are programming language specific,
to web APIs that are designed to leverage the web server and web browser architecture and the implementation is programming language agnostic.
However, APIs (whether traditional or web-based) have some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.

@@

Formal analysis tools, such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in API clients as defects~\cite{lee2012towards}.
These tools typically accept formal representation of the temporal constraints for detecting violations.
However, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API wrapper code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
%in \amazonAPI\ documentation describe temporal constraints.

\textit{The goal of this work is to assist developers construct API clients that comply with
	temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}

Although natural language API description can be manually converted into formal constraints,
manually writing formal constraints based on natural language text in API documents can be prohibitively time consuming and error prone~\cite{wu2013inferring,RubingerWEB10}. 
For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method. Also, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages.

To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
to automatically identify and infer formal temporal constraints. 
We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal temporal constraints from the identified sentences.

@@

First, identifying temporal constraint sentences is difficult. A keyword-based filtering or rule-based approach for identifying constraint sentences is often unsatisfactory, because the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords.
Furthermore, keywords often have confounding effects that inversely affects accuracy.
To, address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.

Second, a method referenced in the natural language text must be identified to infer temporal constraints on the method but such method referencing is often implicit.
Consider the description sentence ``You must initiate a multipart upload before you can upload any part.''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method-invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively resource intensive and error-prone.
To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.

In summary, \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
This paper makes the following main contributions:

>>>>

Application Programming Interfaces (APIs) facilitates software reuse
by providing standardized mechanism to access API components.
However, APIs have some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use and may even result in financial losses.

%Recently, the increasing reach of the internet has fueled the growth of
%web API's, which are designed to leverage the web server and web
%browser architecture and ar eprogramming language agnostic.

@@

Formal analysis tools, such as model checker and runtime verifiers can assist in detection of the violations of the temporal constraints in API clients as defects~\cite{lee2012towards}.
These tools typically accept formal representation of the temporal constraints for detecting violations.
However, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
%in \amazonAPI\ documentation describe temporal constraints.

\textit{The goal of this work is to assist developers construct API clients that comply with
	temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}

Although natural language API description can be manually converted into formal constraints,
manually identifying and writing formal constraints based on natural language text in API documents can be prohibitively time-consuming and error-prone~\cite{wu2013inferring,RubingerWEB10}. 
%For instance, Wu et al.~\cite{wu2013inferring} report that it took one person ten hours to browse the documentation of one method from a web API, even before the person attempted to formalize the constraints on the method. 
For instance, the PDF version of the documentation for \amazonAPI\footnote{{\small \url{http://awsdocs.s3.amazonaws.com/S3/latest/s3-api.pdf}}} spans 278 pages describing 51 methods.

To reduce the manual effort, we propose \tool: a Machine Learning (ML) and Natural Language Processing (NLP) based approach
for identifying and inferring formal temporal constraints. 
We propose to first employ ML for identifying temporal constraint sentences and then use NLP techniques to infer formal temporal constraints from the identified sentences.

@@

First, identifying temporal constraint sentences is difficult.
A naive approach is to perform a keyword-based search.
For instance, consider the sentences from \paypalAPI: 1) ``\textit{Use this call to refund a completed payment.}'' 2) ``\textit{Use this call to complete a payment.}''
Sentence 1 indicates the temporal constraint that a payment must be completed before the refund call is initiated.
In contrast, sentence 2 is a descriptive statement about complete payment method.
Since these sentences are not significantly different in terms of words (sentence 1 contains refund), a simple keyword based approach will fail to distinguish between the two.  
Another problem with keyword based search is that the method names (and synonyms) are part of the keywords themselves, thus resulting in a large number of keywords to be searched.
The large number of keywords often negatively affects accuracy.
%Furthermore, keywords often have confounding effects that inversely affects accuracy.
To address this challenge, we propose to train a classification model based on generic semantic and syntactic features instead of the keywords-based features.

Second, a method referenced in the natural language text must be identified to infer temporal constraints on the method but such method referencing is often implicit.
Consider the description sentence from \amazonAPI: ``\textit{You must initiate a multipart upload before you can upload any part.}''
In this sentence, phrases ``multipart upload'' and ``upload any part'' refer to individual methods in the API.
Identifying these phrases as method-invocation instances requires domain dictionaries.
Ad-hoc construction of such dictionaries is prohibitively resource intensive and error-prone.
To address this challenge, we propose to build domain dictionaries systematically from API documents and generic English dictionaries.

In summary, \tool\ approach leverages natural language description of API's to infer temporal constraints of method invocations.
As our approach analyzes API documents in natural language, it can be reused independent of the programming language of an API library.
Additionally, our approach complements existing mining-based approaches~\cite{buse2012synthesizing, thummalapenta07parseweb, Wang:2013:MSR, Zhong:2009:MMR} that partially address the problem by mining for common usage patterns among client code reusing the API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring 77 formal temporal constraints from these sentences.
This paper makes the following main contributions:

### 2014-12-08 Draft/related.tex
updated based on Dr. Xie's Comments

Additionally, contracts are typically in the form of assertions on the state (member variables/ properties) of a program. In contrast, temporal constraints specify the ordering of method invocations and therefore are different.
Furthermore, since \tool\ infers temporal constraint from API documents, we believe \tool\ can work in conjunction with existing approaches
to infer a comprehensive set of program specifications.

Furthermore, a different set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries. In contrast, \tool\ infers contracts from the natural language text in API documents,
thus complementing these existing approaches when the source code or binaries of the API library is not available.

\textbf{NLP in SE}:
NLP techniques are being increasingly applied in the SE domain. 
Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.
They rely on predefined rule templates targeted towards threading and lock related comments, and then apply ML-based approach to find comments following such rules.
The constraints inferred by their approach are the restrictions imposed by the developer on the client code.
In comparison, the temporal constraints inferred by \tool\ are the restriction imposed by the API library being used by the client code.

Zhong et al.~\cite{zhong09SE} also leverage ML along with type information to infer constraints on resources.
Specifically, their approach infers resource constraints following template: resource creation methods followed by resource manipulation methods followed by resource release methods.
However, temporal constraints may not be limited to such templates. 
Furthermore, the these approaches rely on specific templates for inferring constraints. In contrast, \tool\ works independent of such templates for identifying constraints.

@@

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases.
The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
In contrast, often the sentences in API documents are not well-formed.
Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.

Pandita et al.~\cite{pandita12:inferring} proposed an NLP based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from the their work as follows.
\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach. \tool\ significantly extends the infrastructure used by Pandita et al.~\cite{pandita12:inferring} in following dimensions.
First, \tool\ relies on ML to identify the temporal constraint sentences. The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
Second, approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags only.
Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.

>>>>

Additionally, contracts are typically in the form of assertions on the state (member variables/ properties) of a program. In contrast, temporal constraints specify the ordering of method invocations, therefore are different.
Furthermore, since \tool\ infers temporal constraints from API documents, we envision \tool\ to work in conjunction with existing approaches
to infer a comprehensive formal specification.

A different set of approaches exist that infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries. In contrast, \tool\ infers contracts from the natural language text in API documents,
thus complementing existing approaches when the source code or binaries of the API library is not available.

\textbf{NLP in Software Engineering (SE)}:

Research advances~\cite{Marneffe08COLING,KleinNIPS03} in the accuracy of existing NLP techniques have inspired researchers and practitioners~\cite{pandita12:inferring, pandita13:WHYPER, johnSlankasPASSAT13, XiaoFSE2012, thummalapentaICSE12} to adapt and(/or) apply NLP techniques to solve problems in SE domain. 
Tan et al.~\cite{TanSOSP07} were the first to apply ML and NLP on code comments to detect mismatches between the comments and the implementation.
They rely on predefined rule templates targeted towards threading and lock related comments, and then apply ML-based approach to find comments following such rules.
The constraints inferred by their approach are the restrictions imposed by the developer on the client code.
In comparison, the temporal constraints inferred by \tool\ are the restriction imposed by the API library being used by the client code.

Zhong et al.~\cite{zhong09SE} also leverage ML along with type information to infer constraints on resources from API documents.
Specifically, their approach infers resource constraints following the template - ``\textit{resource creation methods} followed by \textit{resource manipulation methods} followed by \textit{resource release methods}''.
However, temporal constraints are often not be limited to such template. 
Furthermore, the these approaches rely on specific templates for inferring constraints. In contrast, \tool\ works independent of such templates for identifying constraints.

@@

Xiao et al.~\cite{XiaoFSE2012} and Slankas et al.~\cite{johnSlankasPASSAT13} use shallow parsing techniques to infer Access Control Policy (ACP) rules from natural language text in use cases. In contrast, \tool\ approach works with API documents.
%The use of shallow parsing techniques works satisfactorily on natural language text in use cases, owing to relative well-formed structure of sentences in use case descriptions.
%In contrast, often the sentences in API documents are not well-formed.
%Additionally, their approaches do not deal with programming keywords or identifiers, which are often mixed with the method descriptions in API documents.
Pandita et al.~\cite{pandita12:inferring} proposed an NLP-based approach on inferring parameter constraints from method descriptions in the API documents. \tool\ differs from their work as follows.
\tool\ addresses the problem of inferring temporal constraint, which is not addressed by the previous approach. \tool\ significantly extends the infrastructure used by Pandita et al.~\cite{pandita12:inferring} in following dimensions.
First, \tool\ relies on ML to identify the temporal constraint sentences. The lower frequency of occurrence of temporal constraint sentences in comparison to parameter constraint sentences, make them harder to detect.
Second, \tool\ approach introduces hybrid shallow parsing that relies both on parts-of-speech tags as well as Stanford-typed dependencies to construct intermediate representation, while the previous approach relies only on parts-of-speech tags.
Finally, the \tool\ approach leverages the concept of semantic graphs constructed from class and method names in API to automatically infer the implicit method references in a sentence.
